### 2019-06-13 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
Small improvements on layout of abstract/minitoc for chapters

% -----------------------------------------------------------------
\section{Motivation for non stationary MAB models}
\label{sec:6:Introduction}

@@

\textbf{Outline.}
%
% This chapter is structured as follows.
We introduce the model in Section~\ref{sec:6:BanditSetting}, and review related works in Section~\ref{sec:6:relatedWork}.
In Section~\ref{sec:6:ChangePointDetector} we study the Generalized Likelihood Ratio test for sub-Bernoulli distributions (B-GLRT) as a Change-Point Detector (CPD) algorithm.
We introduce the two variants of \GLRklUCB{} algorithm in Section~\ref{sec:6:GLRklUCB_Algorithm}, where we also present upper bounds on the regret of both variants.
The unified regret analysis is given in Section~\ref{sec:6:RegretAnalysis}, we prove one result in Section~\ref{sec:6:proofRegret}.
We discuss numerical experiments in Section~\ref{sec:6:NumericalExperiments}, with more details in the Appendix.

>>>>

% -----------------------------------------------------------------
\section{Motivations for non stationary MAB models}
\label{sec:6:Introduction}

@@

\textbf{Outline.}
%
% This chapter is structured as follows.
We introduce the model in Section~\ref{sec:6:BanditSetting}, and review related works in Section~\ref{sec:6:relatedWork}.
In Section~\ref{sec:6:ChangePointDetector} we study the Generalized Likelihood Ratio test for sub-Bernoulli distributions (B-GLRT) as a Change-Point Detector (CPD) algorithm.
We introduce the two variants of \GLRklUCB{} algorithm in Section~\ref{sec:6:GLRklUCB_Algorithm}, where we also present upper bounds on the regret of both variants.
The unified regret analysis is given in Section~\ref{sec:6:RegretAnalysis}, we prove one result in Section~\ref{sec:6:proofRegret}.
We discuss numerical experiments in Section~\ref{sec:6:NumericalExperiments}, with more details in the Appendix~\ref{sec:6:appendix}.

### 2019-06-13 2-Chapters/Conclusion/conclusion.tex
Small improvements on layout of abstract/minitoc for chapters

% \newpage
\paragraph{Abstract.}
%
This last chapter concludes the thesis, first by summarizing the previous chapters, and by giving a general conclusion of the thesis.
%
We highlight what we consider to be the most important directions of future works, as well as some promising directions that were shortly studied during my PhD but not discussed in the manuscript.

% \vspace*{50pt}

\minitoc

\newpage

@@

% \begin{itemize}
%     \item
The first half, Part~\ref{part:Introduction}, starts by motivating our work and situating the context of this research.
% Chapter 2
In Chapter~\ref{chapter:2}, we present the multi-armed bandit models, the hypotheses we usually make, and the most important algorithms used to solve MAB problems.
% Chapter 3
Then in Chapter~\ref{chapter:3} we discuss in details about our open-source Python library developed to run numerical simulations of MAB problems, SMPyBandits.

    % \item
The second half of this thesis, Part~\ref{part:MABIOT}, presents our main contributions.
% Chapter 4
In Chapter~\ref{chapter:4}, we first propose some models for realistic IoT wireless networks, in discrete times and with no central coordination between end-devices.
% In two different models, with or without retransmissions, we showed that end-devices can learn independently to increase their successful transmission rates in the network, by using low-cost MAB algorithm. We also present a proof-of-concept that implements such network on real radio hardware and validates our model and proposed algorithms.
% Chapter 5
Because the models studied for realistic IoT networks were found to be intractable to analyze from a theoretical point of view, mainly due to the large number of algorithms interacting at random times in a noisy environment,
in Chapter~\ref{chapter:5}, we study a weaker but still interesting model.
We present different variants of the multi-players MAB model, and we propose the state-of-the-art algorithm for the variant with collision information (\MCTopM-\klUCB).
% Chapter 6
Finally, in Chapter~\ref{chapter:6}, we remove the stationary hypothesis on the single-player MAB problem, and we analyze a new actively adaptive algorithm (\GLRklUCB).
%
For the last two chapters, our proposed algorithms attain state-of-the-art performances both on numerical simulations and on the regret bounds obtained in our theoretical analyses.
% \end{itemize}

@@

A few tasks are left on our library SMPyBandits, a first one could be to implement new variants of the single-player stochastic models, as well as variants for the multi-players or the non-stationary cases.
For more details, see the issue tickets at \href{https://github.com/SMPyBandits/SMPyBandits/issues/}{\texttt{GitHub.com/SMPyBandits /SMPyBandits/issues/}}.
%
A second interesting task could be to extend the library for problems with non-finite arms, \eg, linear or contextual bandit (\href{https://github.com/SMPyBandits/SMPyBandits/issues/117}{ticket 117}),
or to add support for the ``dynamic case'' of multi-players bandits to allow arrivals or departures of players (\href{https://github.com/SMPyBandits/SMPyBandits/issues/124}{ticket 124}).
%
A third task that I would have liked to complete is to interface the library with a web-based interactive demonstration, in order to allow anyone to launch simulations without any knowledge of programming.
It is already possible to reproduce some of the experiments presented in this thesis, by using the Jupyter notebooks \cite{jupyter}, hosted on \href{https://perso.crans.org/besson/PhD/notebooks/}{\texttt{perso.crans.org/besson/PhD/notebooks/}}, which can be used locally if one installs or downloads the library, but can also be used on cloud platforms, such as
Binder\footnote{~You can try on \href{https://mybinder.org/v2/gh/SMPyBandits/SMPyBandits/master}{\texttt{mybinder.org/v2/gh/SMPyBandits/SMPyBandits/master}} for free.},
or Google Colab\footnote{~See \href{https://colab.research.google.com/github/SMPyBandits/SMPyBandits/tree/master/notebooks/}{\texttt{colab.research.google.com/github/SMPyBandits/SMPyBandits/tree/master/notebooks/}}.}.

>>>>

% \newpage
\abstractStartChapter{}
%
This last chapter concludes the thesis, first by summarizing the previous chapters, and by giving a general conclusion of the thesis.
%
We highlight what we consider to be the most important directions of future works, as well as some promising directions that were shortly studied during my PhD but not discussed in the manuscript.

\minitocStartChapter{}

@@

\begin{itemize}
    \item
The first half, Part~\ref{part:Introduction}, starts by motivating our work and situating the context of this research.
% Chapter 2
In Chapter~\ref{chapter:2}, we present the multi-armed bandit models, the hypotheses we usually make, and the most important algorithms used to solve MAB problems.
% Chapter 3
Then in Chapter~\ref{chapter:3} we discuss in details about our open-source Python library developed to run numerical simulations of MAB problems, SMPyBandits.

    \item
The second half of this thesis, Part~\ref{part:MABIOT}, presents our main contributions.
% Chapter 4
In Chapter~\ref{chapter:4}, we first propose some models for realistic IoT wireless networks, in discrete times and with no central coordination between end-devices.
% In two different models, with or without retransmissions, we showed that end-devices can learn independently to increase their successful transmission rates in the network, by using low-cost MAB algorithm. We also present a proof-of-concept that implements such network on real radio hardware and validates our model and proposed algorithms.
% Chapter 5
Because the models studied for realistic IoT networks were found to be intractable to analyze from a theoretical point of view, mainly due to the large number of algorithms interacting at random times in a noisy environment,
in Chapter~\ref{chapter:5}, we study a weaker but still interesting model.
We present different variants of the multi-players MAB model, and we propose the state-of-the-art algorithm for the variant with collision information (\MCTopM-\klUCB).
% Chapter 6
Finally, in Chapter~\ref{chapter:6}, we remove the stationary hypothesis on the single-player MAB problem, and we analyze a new actively adaptive algorithm (\GLRklUCB).
%
For the last two chapters, our proposed algorithms attain state-of-the-art performances both on numerical simulations and on the regret bounds obtained in our theoretical analyses.
\end{itemize}

@@

A few tasks are left on our library SMPyBandits, a first one could be to implement new variants of the single-player stochastic models, as well as variants for the multi-players or the non-stationary cases.
For more details, see the issue tickets at \href{https://github.com/SMPyBandits/SMPyBandits/issues/}{\texttt{GitHub.com/SMPyBandits /SMPyBandits/issues/}}.
%
A second interesting task could be to extend the library for problems with non-finite arms, \eg, linear or contextual bandit (\href{https://github.com/SMPyBandits/SMPyBandits/issues/117}{ticket 117}),
or to add support for the ``dynamic case'' of multi-players bandits to allow arrivals or departures of players (\href{https://github.com/SMPyBandits/SMPyBandits/issues/124}{ticket 124}).
%
A third task that I would have liked to complete is to interface the library with a web-based interactive demonstration, in order to allow anyone to launch simulations without any knowledge of programming.
It is already possible to reproduce some of the experiments presented in this thesis, by using the Jupyter notebooks \cite{jupyter}, hosted on \href{https://perso.crans.org/besson/PhD/notebooks/}{\texttt{perso.crans.org/besson/PhD/notebooks/}}, which can be used locally if you install the library, but can also be used on cloud platforms, such as
Binder\footnote{~You can try on \href{https://mybinder.org/v2/gh/SMPyBandits/SMPyBandits/master}{\texttt{mybinder.org/v2/gh/SMPyBandits/SMPyBandits/master}} for free.},
or Google Colab\footnote{~See \href{https://colab.research.google.com/github/SMPyBandits/SMPyBandits/tree/master/notebooks/}{\texttt{colab.research.google.com/github/SMPyBandits/SMPyBandits/tree/master/notebooks/}}.}.
